---
title: "Erasmus Explorer"
output:
  html_document: default
  pdf_document: default
---

write text here

```{r}
library(tidyverse)
Erasmus_mobility_statistics_2014_2019 <- read.csv('Dataset_Erasmus.csv',header = TRUE,  sep = ";")
```

## Nettoyage du dataset

Certaines données sont érronnées. Les ages doivent être compris entre 0 et 122 ans (age du plus viel être humain sur terre). Avant de pouvoir le faire il faut convertir les valeurs numériques.

```{r}
# Conversion
Erasmus_mobility_statistics_2014_2019$Participant.Age <- as.numeric(Erasmus_mobility_statistics_2014_2019$Participant.Age)
Erasmus_mobility_statistics_2014_2019$Mobility.Duration <- as.numeric(Erasmus_mobility_statistics_2014_2019$Mobility.Duration)
# Tri
df <- subset(Erasmus_mobility_statistics_2014_2019, Participant.Age < 122 & Participant.Age > 0)
```

A bar chart showing the distribution of participants by age:
```{r}
df %>%
  group_by(Participant.Age) %>% subset(Participant.Age < 30 & Participant.Age >= 12) %>%
  summarize(Participants = sum(Participants)) %>%
  ggplot(aes(x = Participant.Age, y = Participants, fill = Participants)) +
  geom_col()  + coord_polar() + scale_fill_gradient()+
  theme(axis.text.x = element_text(angle = -50, hjust = 0.25)) + 
  labs( x = "Age des participants", y = "nombre de participants") +
  guides(fill = guide_legend(title = "nombre de participants"))
```
A line chart showing the trend of mobility duration over time:
```{r}
df %>%
  group_by(Academic.Year) %>% summarize(mean_duration = mean(Mobility.Duration)) %>%
  ggplot(aes(x = Academic.Year, y = mean_duration)) +
  geom_col()+
  coord_flip() + 
  labs( y = "Durée moyenne de l'erasmus ( mois )", x = "année académique")
```
A pie chart showing the distribution of participants by gender:
```{r}
df %>%
  group_by(Participant.Gender) %>%
  summarize(Participants = sum(Participants)) %>%
  ggplot(aes(x = "", y = Participants, fill = Participant.Gender)) +
  geom_bar(stat = "identity") +
  scale_y_continuous() +
  coord_polar(theta = "y") + 
  labs( y = "Nombre de participants", x = "") +
  guides(fill = guide_legend(title = "sexe du participant"))

```

A bar chart showing the number of participants by receiving city:
```{r}
data_top10_receiver<- df %>%
  group_by(Receiving.Country.Code) %>%
  summarize(Participant_tot = sum(Participants)) %>%
  top_n(10, Participant_tot)
data_top10_receiver <- data_top10_receiver[order(data_top10_receiver$Participant_tot , decreasing = TRUE), ]
data_top10_receiver$Receiving.Country.Code <- factor(data_top10_receiver$Receiving.Country.Code, levels = data_top10_receiver$Receiving.Country.Code)
data_top10_receiver %>%
  ggplot(aes(x = "", y = Participant_tot, fill= Receiving.Country.Code)) +
  geom_bar(stat = "identity") +
  coord_polar("y") + 
  guides(color = FALSE) + 
  labs( y = "Nombre de participants", x = "") + 
  guides(fill = guide_legend(title = "pays d'accueil"))
```
line chart that show the evolution of participant sent by each country
```{r}
# Select the top 10 nationalities
df_top10 <- df %>%
  group_by(Sending.Country.Code) %>%
  summarize(Participant_tot = sum(Participants)) %>%
  top_n(10, Participant_tot)

# Create a dataset containing only the top 10 nationalities
df_top10_all <- df %>%
  select(everything()) %>%
  inner_join(df_top10, by = "Sending.Country.Code")

# Create the line chart
df_top10_all %>%
  group_by(Academic.Year,Sending.Country.Code) %>% 
  summarize(Participants = sum(Participants)) %>%
  ggplot(aes(x = Academic.Year, y = Participants, color = Sending.Country.Code)) +
  geom_line(aes(group = Sending.Country.Code)) +
  labs( y = "Nombre de participants", x = "année Académique") +
  guides(color = guide_legend(title = "pays de départ"))


```

Nombre de participant envoyé par nations (top 10)
```{r}
data_top10_sender<- df %>%
  group_by(Sending.Country.Code) %>%
  summarize(Participant_tot = sum(Participants)) %>%
  top_n(10, Participant_tot)
data_top10_sender <- data_top10_sender[order(data_top10_sender$Participant_tot , decreasing = TRUE), ]
data_top10_sender$Sending.Country.Code <- factor(data_top10_sender$Sending.Country.Code, levels = data_top10_sender$Sending.Country.Code)
data_top10_sender %>%
  ggplot(aes(x=Sending.Country.Code, y=Participant_tot))+
  geom_point(size=3) + 
  geom_segment(aes(x=Sending.Country.Code, 
                   xend=Sending.Country.Code, 
                   y=0, 
                   yend=Participant_tot))
```

